Pyg4ometry: a python library for the creation of Monte Carlo radiation transport physical geometries

### 2020-02-10 public/paper/pyg4ometry.tex
Fix latex warning about double reference.  Linenumbers. Remove double references in by default.  Include render script.

%% The amssymb package provides various useful mathematical symbols
\usepackage{amssymb}
\usepackage{fancyvrb}
\usepackage[T1]{fontenc}
\PassOptionsToPackage{hyphens}{url}\usepackage{hyperref}
%% The amsthm package provides extended theorem environments
%% \usepackage{amsthm}

@@

{\bf PROGRAM SUMMARY/NEW VERSION PROGRAM SUMMARY}
  %Delete as appropriate.

\begin{small}
\noindent
{\em Program Title: pyg4ometry }                                         		\\
{\em Licensing provisions(please choose one): GPLv3 }			\\
{\em Programming language: python, C/C++}                         		\\

@@

\begin{thebibliography}{0}
\bibitem{1}Reference 1         % This list should only contain those items referenced in the                 
\bibitem{2}Reference 2         % Program Summary section.   
\bibitem{3}Reference 3         % Type references in text as [1], [2], etc.
                               % This list is different from the bibliography at the end of 
                               % the Long Write-Up.
\end{thebibliography}
* Items marked with an asterisk are only required for new versions
of programs previously published in the CPC Program Library.\\
\end{small}

@@

For a logical volume with $n_{\rm daughters}$ physical volumes, assuming meshes for solids with average number of vertices $n$, clearly this algorithm has complexity $\sim \mathcal{O}(n^2 n_{\rm daughters})$. This might seem like a prohibitive computational cost, but worth it considering the potential waste if small overlaps are present in the final 
RT simulation. This algorithm clearly favours geometry descriptions which have a high degree of logical volume reuse. Due to the discrete nature of triangular meshes it is not possible to have perfect detection of overlaps, especially when curved surfaces are considered. 
 \begin{figure}[htbp]
\begin{center}
\includegraphics[width=8cm]{./diagrams/overlap.pdf}
\caption{Placement of physical volume inside a logical volume}
\label{fig:lvToPv}
\end{center}
\end{figure}

>>>>

%% The amssymb package provides various useful mathematical symbols
\usepackage{amssymb}
\usepackage{fancyvrb}
\usepackage[T1]{fontenc}
\PassOptionsToPackage{hyphens}{url}
\usepackage{hyperref}

\usepackage{lineno}
\modulolinenumbers[5]
%% The amsthm package provides extended theorem environments
%% \usepackage{amsthm}

@@

\linenumbers

{\bf PROGRAM SUMMARY}
  %Delete as appropriate.

\begin{small}
\noindent
{\em Program Title: pyg4ometry }                                         		\\
{\em Licensing provisions: GPLv3 }			\\
{\em Programming language: python, C/C++}                         		\\

@@

%\begin{thebibliography}{0}
%\bibitem{1}Reference 1         % This list should only contain those items referenced in the                 
%\bibitem{2}Reference 2         % Program Summary section.   
%\bibitem{3}Reference 3         % Type references in text as [1], [2], etc.
                               % This list is different from the bibliography at the end of 
                               % the Long Write-Up.
%\end{thebibliography}
%* Items marked with an asterisk are only required for new versions
%of programs previously published in the CPC Program Library.\\
\end{small}

@@

For a logical volume with $n_{\rm daughters}$ physical volumes, assuming meshes for solids with average number of vertices $n$, clearly this algorithm has complexity $\sim \mathcal{O}(n^2 n_{\rm daughters})$. This might seem like a prohibitive computational cost, but worth it considering the potential waste if small overlaps are present in the final 
RT simulation. This algorithm clearly favours geometry descriptions which have a high degree of logical volume reuse. Due to the discrete nature of triangular meshes it is not possible to have perfect detection of overlaps, especially when curved surfaces are considered. 
 \begin{figure}[htbp]
\begin{center}
\includegraphics[width=8cm]{./diagrams/overlap.pdf}
\caption{Placement of physical volume inside a logical volume}
\label{fig:overlap}
\end{center}
\end{figure}
